---
title: "assignment3"
author: "Matthew Baker"
date: "February 17, 2019"
output: html_document
---

#include library
library(stringr)

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(stringr)

#raw data
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

#extract only names
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name

#extract phonenumbers
phone <- unlist(str_extract_all(raw.data, "\\(?(\\d{3})?\\)?(-| )?\\d{3}(-| )?\\d{4}"))
phone

df <- data.frame(name = name, phone = phone)
```

#3-1
```{r}
orderedname <- sub("(.+)\\,\\s+(.+)","\\2 \\1", name)
orderedname
df31<- data.frame(name, orderedname)
```

##ordered names
```{r}
df31 
```

##3-2
```{r}
titles <- c("[A-Z]{1}[a-z]{1,}\\.")
matchtitles <- grepl(titles, name)
matchtitles
df32 <- data.frame(name, matchtitles)
```

##Does the character have a title
```{r}
df32
```


#3-3
```{r}
orderedname2 <- orderedname
secondname<-c("[A-Z]{1}[a-z]{0}\\.")
matchsecond<- grepl(secondname, orderedname2)
matchsecond
df33 <- data.frame(orderedname2, matchsecond)
```

##names with a second name
```{r}
df33
```


#4-1
#Number matched at least one time followed by $
```{r}
r1 <- c("[0-9]+\\$")
v1 <-c("1$", "222$", "0123456789$", "abc$", "123", "12#", "ab$")
grepl(r1, v1)
```

#4-2
##set of 1-4 letters
```{r}
r2 <- c("\\b[a-z]{1,4}\\b")
v2<-c("a", "abcd", "1234" , "abcde")
grepl(r2,v2)
```

#4-3
##any string followed by ".txt"
```{r}
r3<-c(".*?\\.txt$")
v3<-c("123.txt", "abc.txt", "123", "abc")
grepl(r3,v3)
```

#4-4
##2 digits forward slash 2 digits forward slash 4 digits
```{r}
r4<-c("\\d{2}/\\d{2}/\\d{4}")
v4 <- c("07/04/1776", "02/17/2019", "1/12/1234", "01/02/123")
grepl(r4, v4)
```

#4-5
##Backreference to match the same text inside angle brackets again with added forward slash
```{r}
r5<-c("<(.+?)>.+?</\\1>")
v5 <- c("<ABC>xxxyyyzzz</ABC>", "<ABC>xxxyyyzzz<ABC>", "ABCxxxyyyzzzABC")
grepl(r5, v5)
```

#9
##cracking code one class as a time
```{r}
msg<-paste("clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr")
msg2 <- gsub(pattern = "[[:digit:]]", replacement = "", msg)
msg3 <- gsub(pattern = "[[:lower:]]", replacement = "", msg2)
msg4 <- gsub(pattern = "\\.", replacement = " ", msg3)
msg4
```
